% Created 2018-02-01 Thu 15:53
\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{mycv}
\usepackage{enumitem}
\setlist{leftmargin=0.25in,nosep}
\setsansfont{Latin Modern Sans}
\setmonofont{Latin Modern Sans}
\linespread{1.5}
\date{}
\title{}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\resheader{ Jaxson Van Doorn }{woofers.github.io}{ jaxson.vandoorn@gmail.com }{ 250-508-2275 }{ 8636 Sentinel Place }{ North Saanich BC }{ V8L 4Z8 }

\section{Projects}
\label{sec-1}
\subsection{Woofers 3D}
\label{sec-1-1}
\subsection{\href{https://github.com/woofers/woofers3d}{github.com/woofers/woofers3d}}
\label{sec-1-2}
\subsubsection{Java}
\label{sec-1-2-1}
\emph{Woofers 3D} is a Java API that attempts to unify the of features Box2D and Bullet Physics into a simpler yet capable package that can be run on nearly any device via LibGDX. Supports modern features such as ray tracing, chasing camera, game states and 3D model importing.
\subsection{Whale}
\label{sec-1-3}
\subsection{\href{https://github.com/woofers/whale}{github.com/woofers/whale}}
\label{sec-1-4}
\subsubsection{Haxe}
\label{sec-1-4-1}
\emph{Whale} is a 2D arcade style game built using HaxeFlixel. It features score tracking, level generation and responsive accelerometer controls. Game is fully completed and can be downloaded from the Google Play Store.
\subsection{Kangaroo Country}
\label{sec-1-5}
\subsection{\href{https://github.com/woofers/kangaroo-country}{github.com/woofers/kangaroo-country}}
\label{sec-1-6}
\subsubsection{Actionscript 3}
\label{sec-1-6-1}
\emph{Kangaroo Country} is a 2D side-scrolling game built in Actionscrpt 3. Game features two fully completed levels where you play as two distinct characters in-order to solve platforming puzzles. As levels are imported from JSON based Tile Editor files, more levels can be dynamically added and created by others.
\subsection{Fox Hole}
\label{sec-1-7}
\subsection{\href{https://github.com/woofers/fox-hole}{github.com/woofers/fox-hole}}
\label{sec-1-8}
\subsubsection{Javascript}
\label{sec-1-8-1}
\emph{Fox Hole} is a 2D proof of concept game built in Javascript with Phaser. You play as a fox sneaking past enemy crocodiles using underground tunnels in order to save your brother. It features checkpoints and enemies complete with very basic AI.
\section{Skills}
\label{sec-2}
\begin{itemize}
\item Experience working with Java, Haxe, Javascript and Git.
\item Ability to quickly adapt to new tools, work-flow and procedures.
\item Comfortable with both Windows, Linux and MacOS command line tools and ecosystems.
\end{itemize}
\section{Experience}
\label{sec-3}
\subsection{Line Cook at \href{https://www.spitfiregrill.ca/}{Spitfire Grill}}
\label{sec-3-1}
\subsubsection{June 2017 - October 2017}
\label{sec-3-1-1}
\textbf{Sidney, BC}
\begin{itemize}
\item Prepare food orders quickly and accurately using the appropriate procedures.
\item Properly maintain and operate commercial grade kitchen equipment.
\item Restock and consolidate inventory in dry and wet storage.
\end{itemize}
\section{Education}
\label{sec-4}
\subsection{BSc, Computer Science at \href{https://www.uvic.ca/}{University of Victoria}}
\label{sec-4-1}
\subsubsection{Sept 2017 - Present}
\label{sec-4-1-1}
\textbf{Victoria, BC}
\begin{itemize}
\item Expecting Graduation in 2021
\end{itemize}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}
